Imputation of Incomplete Multilevel Data with \pkg{mice}

### 2021-12-20 Manuscript/Manuscript.Rmd
Add parameters estimates popularity data

# functions
miceadds::source.all(path = "../R")
`%nin%` <- Negate(`%in%`)
icc <- function(formula, data){multilevel::ICC1(aov(formula, data))}

@@

~~Research into any field with a hierarchical or clustered nature of observations may yield multilevel data. In the typical case, individuals are nested within groups, but there are many different types of multilevel data. In the medical field, clustering occurs at e.g., the hospital or center level in registry data, or at the study-level in meta-analyses (IPDMA). In the social sciences and official statistics we can find clustering e.g. at the country-level, or as imposed by a multi-stage sampling design. For the sake of legibility, we will refer to the grouping variable as 'cluster', and the grouped variable as '(sample) unit' throughout this paper. And, for reasons of brevity, we only discuss clustering between units, not within units (e.g., timeseries or longitudinal data). Also, add that we'll only discuss two levels, not more?~~

@@

```{r patterns, fig.height=3, fig.width=4.1, fig.cap = "Missingness in multilevel data", echo=FALSE}
plot_md_set()
```

@@

# compare ICCs before and after imputation
ICCs <- data.frame(
  vars = c("popular", "popteach", "texp"), 
  incomplete = c(icc(popular ~ class, pop), 
               icc(popteach ~ class, pop),
               icc(texp ~ class, pop)), 
  ignored = c(icc(popular ~ class, complete(imp_ignored)), 
              icc(popteach ~ class, complete(imp_ignored)), 
              icc(texp ~ class, complete(imp_ignored)))
  )
ICCs
```

@@

>>>>

# functions
`%nin%` <- Negate(`%in%`)
icc <- function(formula, data){multilevel::ICC1(aov(formula, data))}
miceadds::source.all(path = "../R")

@@

~~Research into any field with a hierarchical or clustered nature of observations may yield multilevel data. In the typical case, individuals are nested within groups, but there are many different types of multilevel data. In the medical field, clustering occurs at e.g., the hospital or center level in registry data, or at the study-level in meta-analyses (IPDMA). In the social sciences and official statistics we can find clustering e.g. at the country-level, or as imposed by a multi-stage sampling design. For the sake of legibility, we will refer to the grouping variable as 'cluster', and the grouped variable as '(sample) unit' throughout this paper. And, for reasons of brevity, we only discuss clustering between units, not within units (e.g., timeseries or longitudinal data). Also, add that we'll only discuss two levels, not more?~~ Add IPDMA back in: patient level data from multiple studies

@@

```{r patterns, fig.height=3, fig.width=4.1, fig.cap = "Missingness in multilevel data", echo=FALSE}
plot_md_set()
# TODO: make cluster part f the data (blue)
# TODO: dots between 2 and N, for each variable
```

@@

# compare ICCs before and after imputation
ICCs <- data.frame(
  vars = c("popular", "popteach", "texp"), 
  incomplete = c(icc(popular ~ class, pop), 
               icc(popteach ~ class, pop),
               icc(texp ~ class, pop)), 
  ignored = c(icc(popular ~ class, complete(imp_ignored)), 
              icc(popteach ~ class, complete(imp_ignored)), 
              icc(texp ~ class, complete(imp_ignored)))
  )
ICCs

#TODO: think about interactive clusters for the strippplots
#TODO: switch off outliers in boxplot?
```

@@

Here we can set `maxit` to 1...
